---
title: "Statistical_Inference_Part1"
author: "Sharath G"
---


```{r global_options}
    library(knitr)
    library(ggplot2)
    opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

In this analysis, we aim to validate that the mean and variance of the sampling distribution of means of a distribution is related to the population distribution. We also prove that the sampling distribution of means follows a normal distribution, validating central tendency theorem. 

Create a sampling distribution of means from the exponential distribution

```{r}
set.seed(3)
exp_dist <- rep(NA, 1000)

for (i in 1:1000) {
  exp_dist [i] <- mean(rexp(40,0.2))
}

```

Now, let's calculate the mean and the variance of the sampling distribution

```{r}
sample_mean <- mean(exp_dist)
sample_variance <- var(exp_dist)
```

Now, let's calculate the theoretical mean and variance
```{r}
theoretical_mean <- 1/0.2
theoretical_var <- (1/0.2)^2/40
```

We have validated that the theoretical parameters are almost equal to the sample parameters. The sample mean is `r round (sample_mean, 2)` almost equivalent to the theoretical mean `r theoretical_mean`. Similarly, the sample variance is `r round(sample_variance, 2)` almost equivalent to the theoretical variance `r round(theoretical_var, 2)`. 

Now, let's construct a plot to determine if the sampling distibution of means of the exponential distribution is normal. 
```{r}
library(ggplot2)
exp_dist <- data.frame(exp_dist)
names(exp_dist) [1] <- "exponents"
g <- ggplot(exp_dist, aes(exponents))
g <- g + geom_histogram(aes(y = ..density..), fill = "lightblue", binwidth=1/10, color = "blue", lwd = 1)
g <- g + geom_density(lwd = 1, lty = 1, color = "green")
g + geom_vline(xintercept = 5, lwd = 1, lty =2, color = "red")
```

We observe that the distribution of exponents is almost normal, thus validating the central tendency theorem. 


